Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-20 paper/v2.0/sections/1_introduction.tex

In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport.
Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems. However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.

>>>>

In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems. However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.

### 2021-08-20 paper/v2.0/sections/appendix_a.tex

Subsequently we define the \textit{center of the cyclotron orbit} on the $y$-axis as $y_0 = \flatfrac{-p_x}{(eB)}$, and the \textit{cyclotron frequency} as  $\omega_0 = {eB}/{m_e}$. This leads to a new arrangement of the Hamiltonian

>>>>

Subsequently, we define the \textit{center of the cyclotron orbit} on the $y$-axis as $y_0 = \flatfrac{-p_x}{(eB)}$, and the \textit{cyclotron frequency} as  $\omega_0 = {eB}/{m_e}$. This leads to a new arrangement of the Hamiltonian
